### 2021-04-17 paper/ase21/checker.tex
[ASE21] temporal dump
[ASE21] Using IEEEtrans format
[ASE21] Writing Evaluation
[ASE21] More eval.tex

\begin{table}
  \centering
  \caption{Type-related specification bugs fixed by pull requests for the recent
  three years from 2018 to 2021.}
  \label{table:pr-bugs}
  \vspace*{-1.5em}
  \[
    \begin{array}{c|l|r|r}
      \multicolumn{1}{c}{\textbf{Category}} &
      \multicolumn{1}{|c}{\textbf{Bug Kind}} &
      \multicolumn{1}{|c}{\textbf{\# PR}} &
      \multicolumn{1}{|c}{\textbf{\# Bugs}}\\
      \hline

@@

@@

In ECMAScript abstract algorithms, variables are dynamically introduced in any
contexts.  A \textit{reference bug} occurs when trying to access a not yet
defined variable or to redefine an already defined variable.  According to our
manual investigation of pull requests, the reference bug is the most prevalent
type-related specification bugs; \inred{XXX} pull requests fixed \inred{XXX}
unknown variable bugs and \inred{XXX} pull requests fixed \inred{XXX} already
defined variable bugs.  We implement the reference checker by adding additional
checks to abstract semantics of variable lookups $\aseme{\x}$ and variable
declarations $\asemi{\kwlet \; \x = \expr}$ to detect unknown variables and
already defined variables, respectively:
\[
  \begin{array}{r@{~}c@{~}l}
    \aseme{\x}(\aenv) &=& \left\{
      \begin{array}{ll}
        \text{unknown variable} \; $\x$
        & \text{if} \; \asemr{\x}(\aenv) = \{ \tabsent \}\\
        \cdots
        & \text{otherwise}\\
      \end{array}
    \right.\\

@@

Arity $\size{\func}$ of a function $\func = \kwdef \; \f (\p_1, \cdots, \p_n,
\kwsl \cdots, p_m \kwsr). \; \lab$ is defined as an interval $[n, m]$ where $n$
and $m-n$ denote numbers of normal and optional parameters, respectively.  In
function invocations, an \textit{arity mismatch} occurs when the number of
arguments is not matched with the arity of a function, and \inred{XXX} pull
requests fixed \inred{XXX} arity mismatches.  The arity checker detects such
arity mismatches by using additional checks in the abstract semantics of
function call instructions $\asemi{\x = \kwrl \expr_0 \; \expr_1 \cdots \expr_k
\kwrr}$:
\[
  \begin{array}{l}
    \asemi{\x = \kwrl \expr_0 \; \expr_1 \cdots \expr_k \kwrr}(\lab,
    \tys)(\aelem) =\\
    \qquad \left\{
      \begin{array}{ll}
        \text{missing parameters} \; \p_{k+1}, \cdots, \p_{n_\func} &
        \text{if} \; \exists \func \in \aty_0. \; \text{s.t.} \; k < n_\func\\

@@

        \cdots &
        \text{otherwise}\\
      \end{array}
    \right.\\
  \end{array}
\]
where $\func = \kwdef \; \f (\p_1, \cdots, \p_{n_\func}, \kwsl \cdots,
p_{m_\func} \kwsr). \; \lab \wedge \aty_0 = \aseme{\expr_0}(\aelem(\lab,
\tys))$.  For each function $\func$ in the abstract semantics of the function
expression $\expr_0$, the arity checker compares the number of arguments with
the arity $\size{\func}$ to detect arity mismatches.  For example, consider the
lower-left syntax directed algorithm in Figure~\ref{fig:example}.  The algorithm
invocation in line 2 is compiled to a function call instruction:
\[
  \x = \kwrl \code{formal}.\code{IteratorBindingInitialization} \; \code{formal}
  \kwrr
\]
with a temporal variable $\x$.  While it passes only a single argument
$\code{formal}$, the arity of the function
$\code{formal}.\code{IteratorBindingInitialization}$ is $[3, 3]$ thus the arity
checker reports missing parameter bugs for two additional parameters
$\code{iteratorRecord}$ and $\code{environment}$.

\subsection{Assertion Checker}
An \textit{assertion failure} is a specification bug that occurs when the
condition of an assertion instruction is not true.  There were \inred{XXX} pull
requests that fixed \inred{XXX} assertion failures.  The assertion checker
detects such bugs using additional checks in the abstract semantics of assertion
instructions $\asemi{\kwassert \; \expr}$:
\[
  \asemi{\kwassert \; \expr}(\lab, \tys)(\aelem) = \left\{
    \begin{array}{ll}
      \text{assertion failure} \; \expr &
      \text{if} \; \{ \true \} \norder \aty\\

@@

Several operators are typed and a \textit{wrong typed operand bug} occurs when
the type of an operand is not conform to the expected type.  For example, the
comparison operator $\code{<}$ is a numeric operator in the modified $\ires$.  If
an expression tries to compare between non-numeric values such as $\true <
\code{"abc"}$, then it is a non-numeric operand bug.  Besides, ECMAScript has a
special implicit conversion for normal completions when their actual values
stored in the $\code{Value}$ field are required including conditions, values of
field updates, operands of operators, etc.  For example, if the variable $\x$
has a normal completion with 42 as its actual value, $\x + 1$ should 43 because
the normal completion implicitly converted into its actual value 42.  To
explicitly represent this conversion, let's define a unary operator $\escaped$:
\[
  \escaped \val = \left\{
    \begin{array}{ll}
      \val.\code{Value} &
      \text{if} \; \val \; \text{is a normal completion}\\

@@

The operand checker detects such wrong typed operand bugs by using additional
checks in the abstract semantics of binary operations $\aseme{\expr \bop \expr}$
or unary operations $\aseme{\uop \; \expr}$:
\[
  \begin{array}{r@{~}c@{~}l}
    \aseme{\expr_0 \bop \expr_1}(\aenv) &=& \left\{
      \begin{array}{ll}
        \text{wrong typed operand} \; \expr_0
        & \text{if} \; \asemr{\expr_0}(\aenv) \norder \aty_0\\
        \text{wrong typed operand} \; \expr_1
        & \text{if} \; \asemr{\expr_1}(\aenv) \norder \aty_1\\
        \cdots
        & \text{otherwise}\\
      \end{array}
    \right.\\

    \aseme{\uop \; \expr}(\aenv) &=& \left\{
      \begin{array}{ll}
        \text{wrong typed operand} \; $\expr$
        & \text{if} \; \asemr{\expr}(\aenv) \norder \aty\\
        \cdots
        & \text{otherwise}\\
      \end{array}
    \right.\\
  \end{array}
\]
where $\aty$, $\aty$, and $\aty$ are expected abstract types of $\expr_0$,
$\expr_1$, and $\expr$, respectively.  The additional check reports when the
given operand does not conform to the expected types.  For example, consider the
upper-right built-in algorithm $\code{Math.round}$ in Figure~\ref{fig:example}.
The parameter $\x$ has $\{ \tjs \}$ and $\n$ has $\{ \tnum \}$ because the
\textbf{ToNumber} algorithm always return number values or abrupt completions
but later cases are removed by the \textbf{ReturnIfAbrupt} prefix ?.  While the
built-in algorithm correctly uses $\n$ in line 2, it misuses $\x$ in line 3 and
4 and $\{ \tjs \}$ does not have a partial order with the expected abstract type
$\{ \tnum, \tbigint \}$.  Thus, the operand type checker reports non-numeric
operand bugs.

>>>>

\begin{table}
  \centering
  \caption{Type-related specification bugs fixed by pull requests for the recent
  three years from 2018 to 2021.}
  \label{table:pr-bugs}
  \vspace*{-1.5em}
  \[
    \small
    \begin{array}{c|l|r|r}
      \multicolumn{1}{c|}{\textbf{Category}} &
      \multicolumn{1}{c|}{\textbf{Bug Kind}} &
      \multicolumn{1}{c|}{\textbf{\# PR}} &
      \multicolumn{1}{c}{\textbf{\# Bugs}}\\
      \hline

@@

% TODO: more detail of investigation

@@

In ECMAScript abstract algorithms, variables are dynamically introduced in any
contexts.  A \textit{reference bug} occurs when trying to access a not yet
defined variable or to redefine an already defined variable.  According to our
manual investigation of pull requests, the reference bug is the most prevalent
type-related specification bugs; \inred{XXX} pull requests fixed \inred{XXX}
unknown variable bugs and \inred{XXX} pull requests fixed \inred{XXX} already
defined variable bugs.  We implement the reference checker by adding additional
checks to abstract semantics of variable lookups $\aseme{\x}$ and variable
declarations $\asemi{\kwlet \; \x = \expr}$ to detect unknown variables and
already defined variables, respectively:
\[
  \small
  \begin{array}{r@{~}c@{~}l}
    \aseme{\x}(\aenv) &=& \left\{
      \begin{array}{ll}
        \text{unknown variable} \; $\x$
        & \text{if} \; \asemr{\x}(\aenv) = \{ \tabsent \}\\
        \cdots
        & \text{otherwise}\\
      \end{array}
    \right.\\

@@

Arity $\size{\func}$ of a function $\func = \kwdef \; \f (\p_1, \cdots, \p_n,
\kwsl \cdots, p_m \kwsr). \; \lab$ is defined as an interval $[n, m]$ where $n$
and $m-n$ denote numbers of normal and optional parameters, respectively.  In
function invocations, an \textit{arity mismatch} occurs when the number of
arguments is not matched with the arity of a function, and \inred{XXX} pull
requests fixed \inred{XXX} arity mismatches.  The arity checker detects such
arity mismatches by using additional checks in the abstract semantics of
function call instructions $\asemi{\x = \kwrl \expr_0 \; \expr_1 \cdots \expr_k
\kwrr}$:
\[
  \small
  \begin{array}{l}
    \asemi{\x = \kwrl \expr_0 \; \expr_1 \cdots \expr_k \kwrr}(\lab,
    \tys)(\aelem) =\\
    \qquad \left\{
      \begin{array}{ll}
        \text{missing parameters} \; \p_{k+1}, \cdots, \p_{n_\func} &
        \text{if} \; \exists \func \in \aty_0. \; \text{s.t.} \; k < n_\func\\

@@

        \cdots &
        \text{otherwise}\\
      \end{array}
    \right.\\
  \end{array}
\]
where $\func = \kwdef \; \f (\p_1, \cdots, \p_{n_\func}, \kwsl \cdots,
p_{m_\func} \kwsr). \; \lab \wedge \aty_0 = \aseme{\expr_0}(\aelem(\lab,
\tys))$.  For each function $\func$ in the abstract semantics of the function
expression $\expr_0$, the arity checker compares the number of arguments with
the arity $\size{\func}$ to detect arity mismatches.  For example, consider the
lower-left syntax directed algorithm in Figure~\ref{fig:example}.  The algorithm
invocation in line 2 is compiled to a function call instruction:
\[
  \small
  \x = \kwrl \code{formal}.\code{IteratorBindingInitialization} \; \code{formal}
  \kwrr
\]
with a temporal variable $\x$.  While it passes only a single argument
$\code{formal}$, the arity of the function
$\code{formal}.\code{IteratorBindingInitialization}$ is $[3, 3]$ thus the arity
checker reports missing parameter bugs for two additional parameters
$\code{iteratorRecord}$ and $\code{environment}$.

\subsection{Assertion Checker}
An \textit{assertion failure} is a specification bug that occurs when the
condition of an assertion instruction is not true.  There were \inred{XXX} pull
requests that fixed \inred{XXX} assertion failures.  The assertion checker
detects such bugs using additional checks in the abstract semantics of assertion
instructions $\asemi{\kwassert \; \expr}$:
\[
  \small
  \asemi{\kwassert \; \expr}(\lab, \tys)(\aelem) = \left\{
    \begin{array}{ll}
      \text{assertion failure} \; \expr &
      \text{if} \; \{ \true \} \norder \aty\\

@@

\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/func}
    \caption{The number of functions.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/view}
    \caption{The number of views.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/iter}
    \caption{The number of iterations.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/time}
    \caption{The analysis time.}
  \end{subfigure}
  \caption{The statistics of type analysis using $\tool$ for 864 versions of
  ECMAScript.}
  \vspace*{-1.5em}
  \label{fig:stat}
\end{figure*}

Several operators are typed and a \textit{wrong typed operand bug} occurs when
the type of an operand is not conform to the expected type.  For example, the
comparison operator $\code{<}$ is a numeric operator in the modified $\ires$.  If
an expression tries to compare between non-numeric values such as $\true <
\code{"abc"}$, then it is a non-numeric operand bug.  Besides, ECMAScript has a
special implicit conversion for normal completions when their actual values
stored in the $\code{Value}$ field are required including conditions, values of
field updates, operands of operators, etc.  For example, if the variable $\x$
has a normal completion with 42 as its actual value, $\x + 1$ should 43 because
the normal completion implicitly converted into its actual value 42.  To
explicitly represent this conversion, let's define a unary operator $\escaped$:
\[
  \small
  \escaped \val = \left\{
    \begin{array}{ll}
      \val.\code{Value} &
      \text{if} \; \val \; \text{is a normal completion}\\

@@

The operand checker detects such wrong typed operand bugs by using additional
checks in the abstract semantics of binary operations $\aseme{\expr \bop \expr}$
or unary operations $\aseme{\uop \; \expr}$:
\[
  \small
  \begin{array}{r@{~}c@{~}l}
    \aseme{\expr_0 \bop \expr_1}(\aenv) &=& \left\{
      \begin{array}{ll}
        \text{wrong typed operand} \; \expr_0
        & \text{if} \; \asemr{\expr_0}(\aenv) \norder \aty_0\\
        \text{wrong typed operand} \; \expr_1
        & \text{if} \; \asemr{\expr_1}(\aenv) \norder \aty_1\\
        \cdots
        & \text{otherwise}\\
      \end{array}
    \right.\\

    \aseme{\uop \; \expr}(\aenv) &=& \left\{
      \begin{array}{ll}
        \text{wrong typed operand} \; $\expr$
        & \text{if} \; \asemr{\expr}(\aenv) \norder \aty\\
        \cdots
        & \text{otherwise}\\
      \end{array}
    \right.\\
  \end{array}
\]
where $\aty_0$, $\aty_1$, and $\aty$ are expected abstract types of $\expr_0$,
$\expr_1$, and $\expr$, respectively.  The additional check reports when the
given operand does not conform to the expected types.  For example, consider the
upper-right built-in algorithm $\code{Math.round}$ in Figure~\ref{fig:example}.
The parameter $\x$ has $\{ \tjs \}$ and $\n$ has $\{ \tnum \}$ because the
\textbf{ToNumber} algorithm always return number values or abrupt completions
but later cases are removed by the \textbf{ReturnIfAbrupt} prefix ?.  While the
built-in algorithm correctly uses $\n$ in line 2, it misuses $\x$ in line 3 and
4 and $\{ \tjs \}$ does not have a partial order with the expected abstract type
$\{ \tnum, \tbigint \}$.  Thus, the operand type checker reports non-numeric
operand bugs.

### 2021-04-17 paper/ase21/eval.tex
[ASE21] Minor change in evaluation
[ASE21] More eval.tex

\begin{figure*}
  \centering
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/func}
    \caption{The number of functions.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/view}
    \caption{The number of views.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/iter}
    \caption{The number of iterations.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/time}
    \caption{The analysis time.}
  \end{subfigure}
  \caption{The statistics of $\tool$ for each version of ECMAScript.}
  \label{fig:stat}
\end{figure*}

To evaluate $\tool$, we answer the following research questions:
\begin{itemize}
  \item RQ1. \textbf{(Performance)} How long does $\tool$ take to perform type
    analysis for JavaScript specifications?
  \item RQ2. \textbf{(Precision)} How many type-related specification bugs
    detcted by $\tool$ are true bugs?
  \item RQ3. \textbf{(Effect of Refinement)} Does the condition-based refinement
    improve the analysis precision with endurable performance degradation?
  \item RQ4: \textbf{(Detection of New Bugs)} Does $\tool$ detect new
    specification bugs in the latest version of ECMAScript?
\end{itemize}
The draft of the next version of ECMAScript (ES12, 2021) is fixed on March 9,
2021.  Thus, we targeted all different \inred{864} versions existed in the
official ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for
the recent three years from January 1, 2018 to March 9, 2021.  We performed our
experiments on five Ubuntu machines equipped with 4.2GHz Quad-Core Intel Core i7
and 32GB of RAM.

To evaluate the performance of $\tool$, we measured the analysis time for
\inred{864} versions of ECMAScript.  For each version, we assigned an unsigned
integer as its unique identifier in chronological order starting from 1; the
identifier of the oldest version is 1 and that of the latest version is
\inred{864}.  Figure~\ref{fig:time} depicts the analysis time of $\tool$ for
each version in chronological order.  The dark gray, blue, and red bars
represent times of specification extraction (\code{extract}), type analysis
(\code{analyze}), and bug detection (\code{detect}), respectively.  $\tool$ took
\inred{XXX.XX} seconds to analyze each version of ECMAScript on average; the
specification extraction took \inred{XX.XX} seconds (\inred{XX.XX}\%), the type
analysis took \inred{XX.XX} seconds (\inred{XX.XX}\%), and the bug detection
took \inred{XX.XX} seconds (\inred{XX.XX}\%) on average.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/compare-time}
    \caption{The analysis time.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/ratio-time}
    \caption{The ratio of analysis time.}
  \end{subfigure}
  \caption{The comparison between analysis time without and without condition-based
  refinement.}
  \label{fig:refine}
\end{figure}

\begin{table*}
  \centering
  \[
    \footnotesize
    \begin{array}{c|c?c|c?c|c?c|c}
      \multirow{2}{*}{\textbf{Checker}} &
      \multirow{2}{*}{\textbf{Bug Kind}} &
      \multicolumn{6}{c}{
        \textbf{Precision = (\# True Bugs) / (\# Total Bugs)}
      }\\\cline{3-8} &&
      \multicolumn{2}{c?}{\text{no-refine}} &
      \multicolumn{2}{c?}{\text{refine}} &
      \multicolumn{2}{c}{\Delta}\\\hline\hline

@@

      \hline\hline

      \mysrowh
      {Total}         {43/44 (97.7\%)}  {43/44 (97.7\%)}  {\md{12}{3}{51.7}}

    \end{array}
  \]
  \caption{The analysis precision of $\tool$ without and with condition-based
  refinement.}
  \label{fig:refine}
\end{table*}

  Moreover, Figure~\ref{fig:function}
represents the number of functions analyzed by $\tool$ for each version of
ECMAScript; the gray and dark gray bars denote numbers of partially and fully
compiled functions, respectively.  On average, \inred{XXXX} functions are
analyzed by $\tool$ thus

Figure~\ref{fig:function}
Figure~\ref{fig:time}

$\tool$ consists of three steps:
specification extraction, type analysis, and bug detection, and we measured the
duration time

For different \inred{864} versions of ECMAScript,

We evaluated performance

@@

@@

\subsection{Impact}

>>>>

\begin{table*}
  \centering
  \caption{The analysis precision of $\tool$ without and with condition-based
  refinement.}
  \label{fig:refine}
  \resizebox{\textwidth}{!}{%
  \begin{tabular}{c|c?c|c?c|c?c|c}
    \multirow{2}{*}{\textbf{Checker}} &
    \multirow{2}{*}{\textbf{Bug Kind}} &
    \multicolumn{6}{c}{
      \textbf{Precision = (\# True Bugs) / (\# Total Bugs)}
    }\\\cline{3-8} &&
    \multicolumn{2}{c?}{no-refine} &
    \multicolumn{2}{c?}{refine} &
    \multicolumn{2}{c}{$\Delta$}\\

    \specialrule{.1em}{.0em}{.0em}

@@

    \specialrule{.1em}{.0em}{.0em}

    \mysrowh
    {\textbf{Total}}{43 / 44 (97.7\%)}  {43 / 44 (97.7\%)}  {\md{12}{3}{51.7}}

  \end{tabular}
  }
\end{table*}

To evaluate $\tool$, we answer the following research questions:
\begin{itemize}
  \item RQ1. \textbf{(Performance)} How long does $\tool$ take to perform type
    analysis for JavaScript specifications?
  \item RQ2. \textbf{(Precision)} How many type-related specification bugs
    detcted by $\tool$ are true bugs?
  \item RQ3. \textbf{(Effect of Refinement)} Does the condition-based refinement
    improve the analysis precision with endurable performance degradation?
  \item RQ4: \textbf{(Detection of New Bugs)} Does $\tool$ detect new
    specification bugs in the latest version of ECMAScript?
\end{itemize}
The draft of the next version of ECMAScript (ES12, 2021) is fixed on March 9,
2021.  Thus, we targeted all different 864 versions existed in the official
ECMAScript repository~\footnote{https://github.com/tc39/ecma262} for the recent
three years from January 1, 2018 to March 9, 2021.  We performed our experiments
on five Ubuntu machines equipped with 4.2GHz Quad-Core Intel Core i7 and 32GB of
RAM.

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/ttl-chro}
    \caption{TTL sorted by creation time.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/ttl-count}
    \caption{True bugs classfied by TTL.}
  \end{subfigure}
  \caption{Time to Live (TTL) of true bugs.}
  \vspace*{-1.5em}
  \label{fig:ttl}
\end{figure}

Figure~\ref{fig:stat} shows four statistics of type analysis using $\tool$ for
864 versions of ECMAScript: (a) the number of analyzed functions, (b) the number
of flow- and type-sensitive views, (c) the number of worklist iteration, and (d)
the analysis time.  For each version of ECMAScript, \inred{1,999.9} functions
(\textsf{func}) are analyzed and \inred{1,999.9} functions among them are fully
compiled (\textsf{full-func}) on average.  Since the compile rules in $\jiset$
is more suitable for recent versions, the number of fully compiled functions in
older versions are less than in more recent versions.  $\tool$ keeps different
abstract environments for each functions divided by flow- and type-sensitive
views.  In the analysis result, \inred{1.3}M views existed for each version and
\inred{1.3}K views existed for each function on average.

We measured performance of $\tool$ based on the number of iteration for worklist
algorithm and the analysis time.  For each version of ECMAScript, $\tool$ took
\inred{300.0} seconds with \inred{19,999.9} iterations of worklist algorithm on
average.  The analysis time consists of \inred{10.0} seconds for the
specification extraction (\textsf{extract}), \inred{340.0} seconds for the type
analysis (\textsf{analyze}), \inred{10.0} seconds for the bug detection
(\textsf{detect}).

\begin{table}
  \centering
  \caption{The creaters and resolvers of true bugs.}
  \label{fig:author}
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{c|c|c?c|c|c}
    \multicolumn{3}{c?}{\textbf{Creater}} &
    \multicolumn{3}{c}{\textbf{Resolver}}\\\hline

    \textbf{Committee} &
    \textbf{Outsider} &
    \textbf{Inherited} &
    \textbf{Committee} &
    \textbf{Outsider} &
    \textbf{NotYet}\\\hline

    \inred{60} &
    \inred{12} &
    \inred{20} &
    \inred{60} &
    \inred{23} &
    \inred{10}\\
  \end{tabular}
  }
\end{table}

@@

\begin{figure}
  \centering
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/compare-iter}
    \caption{The number of iterations.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/ratio-iter}
    \caption{The ratio of iterations.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/compare-time}
    \caption{The analysis time.}
  \end{subfigure}
  \begin{subfigure}[b]{0.24\textwidth}
    \includegraphics[width=\textwidth]{img/ratio-time}
    \caption{The ratio of analysis time.}
  \end{subfigure}
  \caption{The comparison of iterations and analysis time without and with
  condition-based refinement.}
  \label{fig:refine}
\end{figure}

@@

\subsection{Detection of New Bugs}

\begin{table*}
  \centering
  \caption{Type-related specification bugs newly detected by $\tool$ in the
  official draft of ECMAScript 2021 (ES12).}
  \label{fig:new-bug}
  \resizebox{\textwidth}{!}{%
  \begin{tabular}{@{}c@{~}?c|@{~}c@{~}|l|c|@{~}c@{~}|@{~}c@{~}|@{~}r@{}}
    \multicolumn{1}{@{}c?}{\textbf{Name}} &
    \multicolumn{1}{c}{\textbf{Feature}} &
    \multicolumn{1}{@{}c@{~}}{\textbf{\#}} &
    \multicolumn{1}{c}{\textbf{Description}} &
    \multicolumn{1}{@{~}c@{~}}{\textbf{Checker}} &
    \multicolumn{1}{@{}c}{\textbf{Created}} &
    \multicolumn{1}{@{}c}{\textbf{Resolved}} &
    \multicolumn{1}{@{}c@{~}}{\textbf{TTL}}\\\specialrule{.1em}{.0em}{.0em}

    ES12-1 &
    Switch &
    3 &
    \makecell[l]{
        Variables \code{hasDuplicates} and \code{hasUndefinedLabels} are already
        defined \\ in algorithms for \jscode{case} blocks of \jscode{switch}
        statements.
    } &
    Reference &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-2 &
    Try &
    3 &
    \makecell[l]{
        Variables \code{hasDuplicates} and \code{hasUndefinedLabels} are already
        defined \\ in algorithms for \jscode{try} statements.
    } &
    Reference &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-3 &
    Arguments &
    1 &
    \makecell[l]{
        A variable \code{index} is already defined in
        \textbf{CreateMappedArgumentsObject}.
    } &
    Reference &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-4 &
    Array &
    2 &
    \makecell[l]{
        A variable \code{succeeded} is already defined in algorithms for
        \jscode{Array} objects.
    } &
    Reference &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-5 &
    Class &
    1 &
    \makecell[l]{
        A variable \code{ClassHeritage} is not defined in \textbf{Contains}
        \\ for tails of \jscode{class} declarations.
    } &
    Reference &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-6 &
    Branch &
    1 &
    \makecell[l]{
        A variable \code{Statement} is not defined in \textbf{EarlyErrors} for
        \jscode{if} statement.
    } &
    Reference &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-7 &
    Async &
    1 &
    \makecell[l]{
        A variable \code{value} is already defined in \textbf{Evaluation} for
        \jscode{yield} expressions.
    } &
    Reference &
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\\hline

    ES12-8 &
    Arguments &
    2 &
    \makecell[l]{
        The result of the \textbf{Get} algorithm is used without checking of
        abrupt completions \\ in \textbf{DefineOwnProperty} and
        \textbf{GetOwnProperty} for \jscode{arguments} objects.
    } &
    \makecell[c]{
      Operand \\ Type
    }&
    \inred{2015-01-01} &
    \inred{2015-01-01} &
    \inred{1,999} days\\
  \end{tabular}
  }
\end{table*}
